### 2022-03-07 paper/fse22/approach.tex
approach

\begin{figure*}
  \centering
  \includegraphics[scale=0.5]{figs/overall.pdf}
  \vspace{-5pt}
  \caption{\OverallModelFigCaption}
  \vspace{-10pt}
\end{figure*}

@@

\begin{figure}[t]
  \lstinputlisting[language=json-pretty]{code/requirement_sa1.json}
  \vspace{-10pt}
  \caption{\SearchRequirementExampleFigCaption}
  \vspace{-10pt}
\end{figure}

\begin{figure}[t]
  \lstinputlisting[language=json-pretty]{code/requirement_sa2.json}
  \vspace{-10pt}
  \caption{\TransformRequirementExampleFigCaption}
  \vspace{-10pt}
\end{figure}

Figure~\ref{fig:SearchReqEx} shows \lc of \SareqExOne. To evaluate
this \lc, the input is required to be short and have only \neu \adjs,
\neu \nns. In addition, the label needs to be \neu. Therefore, all
short natural \sents with only \neu \adjs and \neu \nns are available
to evaluate NLP models. Next, transform \req explains how the input
and output needs to be tranfromed. Some \lc only accepts heavily
limited input distribution, and it is unlikely to be included in
searching dataset because of its high structural diversity. Therefore,
our approach is to find inputs by relaxing search requirement and
transform the input to match the target requirement of the \lc. In
this work, the inputs are transformed by word addition or perturbing
the found inputs with \lc dependent templates. \Lc of \SareqExTwo in
the figure~\ref{fig:TransformReqEx}, for instance, requires inputs to
be the negated \pstv \sents and be the neutral expression in the
middle. Finding such \sents is costly because such sentneces are
diverse in terms of their structure. Rather, the \Model search \pstv s
and \neu inputs and combine them into negated \pstv \sents. The
transformation of inputs produce the transformed inputs in
distribution on \lc and high diversity in the inputs because of that
from initially found inputs.

\subsection{Seed parsing phase}
In the seed parsing phase,

\subsection{Reference phase}

\subsection{Syntax expansionphase}

>>>>

\begin{figure*}
  \centering
  \includegraphics[scale=0.5]{figs/overview.pdf}
  \vspace{-5pt}
  \caption{\OverallModelFigCaption}
  \vspace{-10pt}
\end{figure*}

@@

\begin{figure}[t]
  \centering
  \lstinputlisting[language=json-pretty]{code/requirement_sa1.json}
  \vspace{-10pt}
  \caption{\SearchRequirementExampleFigCaption}
  \vspace{-10pt}
\end{figure}

\begin{figure}[t]
  \centering
  \subfloat[][\TransformRequirementExampleSubFigCaption]{\lstinputlisting[language=json-pretty]{code/requirement_sa2.json}}
  \\
  \subfloat[][\TransformTemplateExampleSubFigCaption]{\lstinputlisting[language=python-pretty]{code/requirement_sa2.py}}
  \\
  \caption{\TransformRequirementExampleFigCaption}
  \vspace{-10pt}
\end{figure}

Figure~\ref{fig:SearchReqEx} shows \lc of \SareqExOne. To evaluate
this \lc, the input is required to be short and have only \neu \adjs,
\neu \nns. In addition, the label needs to be \neu. Therefore, all
short natural \sents with only \neu \adjs and \neu \nns are available
to evaluate NLP models. Next, transform \req explains how the input
and output needs to be tranfromed. Some \lc only accepts heavily
limited input distribution, and it is unlikely to be included in
searching dataset because of its high structural diversity, thus,
finding such \sents is costly. Therefore, our approach is to find
inputs by relaxing search requirement and transform the input to match
the target requirement of the \lc. In this work, the inputs are
transformed by word addition or perturbing the found inputs with \lc
dependent templates. The figure~\ref{fig:TransformReqEx} shows the
example of use of the template requirement. The \lc of \SareqExTwo in
the figure~\ref{fig:TransformReqSubEx} requires inputs to be the
negated \pstv \sents and the neutral expression in the middle. Rather
than searching \sents that match the input distribution of the \lc,
the \Model search \pstv and \neu inputs and combine them into negated
\pstv \sents. Figure~\ref{fig:TransformTempSubEx} illustrates template
for the \lc. According to the \lc, The value of ``sent1'' and
``sent2'' become each searched \neu and \pstv inputs respectively, and
the template completion generates new inputs that matches the target
\lc. In addition, the transformation of inputs also produce high
diversity in the inputs because of that from initially found
inputs. In this paper, we will denote the searched inputs in this
phase as seed inputs.

\subsection{Seed parsing phase}
To expands seed sentence and generate fluent and faithful sentence
used for evaluation, \Model studies structure of each seed input for
its expansion. To extract the structure, this phase takes each seed as
input, and the parse tree of the seed input is output.  In this phase,
\Model implements the Berkeley Neural
Parser~\cite{kitaev2018seedparser,kitaev2019seedparser}.

\subsection{Reference phase}
In this phase, we take a large scale corpus as reference. We assume
that large corpus represents data distribution of real world,
the descripancy comparing seed sentence with the reference

structural information reference corpus is also parsed into \cfg.

\subsection{Syntax expansion phase}
